\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\usepackage{eurosym}
\begin{document}

%====================
% BOOKING.COM
%====================
\subsection{{\large\href{https://booking.com}{Booking.com}}}
\subtext{Senior Software Engineer \hfill April 2023 --- Present}



\begin{zitemize}

\item \textbf{Technically led} the integration with Citi bank, overseeing collaboration across multiple business units and leveraged the team by delegating
independent project pieces to developers.

\item Directed the integration with PayPal and owned stakeholder management across multiple departments, resulting in
\textbf{seamless \euro 700M annual payments.}

\item Enhanced the pipeline for collecting code quality metrics, developed a quality gate based on these metrics, and implemented it
\textbf{across 22 services department-wide.}

\item Improved the partner payment experience, resulting in an \textbf{annual TTV increase of \euro 29.3M} and a reduction in cancellations
\textbf{worth \euro 30K annually}.

\end{zitemize}

%====================
% YANDEX
%====================
\subsection{{\large\href{https://yandex.com/}{Yandex}}}
\subtext{Senior Software Engineer \hfill May 2021 --- March 2023}

\begin{zitemize}
\item \textbf{Technically led} the payment system launch, supporting the transaction volume growth from \textbf{\$12K to \$2.4M annually}.

\item  Pioneered the design of an event-sourcing architecture for the payments, ensuring seamless scalability and \textbf{zero downtime}.

\item  Built \textbf{Know Your Customer (KYC)} processes from scratch, integrating with external services to guarantee secure and compliant user verification.

\item  Designed and developed a housing and communal services module, resulting in a \textbf{15\% revenue increase}.

\item  Established gRPC-based API contracts, streamlining \textbf{cross-team communication} and ensuring consistency across the system.
\end{zitemize}


%====================
% HAULMONT
%====================
\subsection{{\large\href{https://www.haulmont.com/}{Haulmont}}}
\subtext{{Technical Lead \hfill February 2020 --- May 2021}}



\begin{zitemize}
\item Led a team of \textbf{5 developers} to successfully complete \textbf{2 projects}, ensuring timely delivery and alignment with project goals

\item Decreased the \textbf{latency of hard processes by 40\%} through the implementation of caching and optimization techniques

\item Assembled highly complex reports logic based on the Cuba framework and YAML in a very short timeframe, addressing critical business requirements.

\end{zitemize}


%====================
% DD
%====================
\subsection{{\large\href{https://www.digdes.com/}{Digital Design}}}
\subtext{{Senior Software Engineer\hfill June 2018 --- August 2019}}


\begin{zitemize}
\item \textbf{Technically led} a team of \textbf{3 developers} to successfully design and launch a document management system in a short timeframe.
\end{zitemize}


%====================
% EPAM
%====================
\subsection{{\large\href{https://www.epam.com/}{EPAM Systems}}}
\subtext{{Software Engineer \hfill June 2017 --- June 2018}}
\begin{zitemize}
\item Investigated and optimized opaque business logic for discounting in the POS system.
\end{zitemize}


%====================
% Exactpro
%====================
\subsection{{\large\href{https://exactpro.com/}{Exactpro Systems}}}
\subtext{{Software Engineer\hfill October 2015 --- May 2017}}
\begin{zitemize}
\item Provided end-to-end and unit tests for entire project with \textbf{86\% coverage}.
\end{zitemize}
%====================
% Neoflex
%====================
\subsection{{\large\href{https://www.neoflex.ru/}{Neoflex}}}
\subtext{{Junior Software Engineer\hfill July 2013 --- February 2015}}
\begin{zitemize}
\item Provided and supported Jira plugins and special reports for internal infrastructure system.
\end{zitemize}

\end{document}